
\documentclass[10pt]{article}

\usepackage{../template/grimdark}

\mytitle{High Elf Fleets v1.2}
\begin{document}

\UnitTable{1}

\begin{multicols*}{3}[]
	\begin{center}

		\UpgradeGroups{1}{O}

		\specialrules
		\sprule{Council}{This unit counts as having Psychic(X),
		where X is the number of models in it. Only one
		model may use psychic spells per round.}
		\sprule{Teleport}{This model may teleport instead of
		moving normally. Place the model within 2D6" of
		its starting position, ignoring units and terrain.}
		\sprule{Very Fast}{This model moves 12" when using
		Advance and 24" when using Rush/Charge.}

		\startpsychic{
		\psychic{Hide}{2+}{Target friendly unit within 12" gets Stealth until the end of the round.}
		\psychic{Seek}{2+}{Target enemy unit within 18" loses the effect of cover until the end of the round.}
		\psychic{Creator}{4+}{Target friendly model within 18" may heal 1 wound.}
		\psychic{Destroyer}{5+}{Target enemy unit within 12" takes D6 automatic hits with AP(1).}
		\psychic{Blessing}{5+}{Target friendly unit within 24" gets Defense +1 until the end of the round.}
		\psychic{Storm}{6+}{Target enemy unit within 24" takes D6 automatic hits with Poison(1).}
		}


	\end{center}
\end{multicols*}
\pagebreak

\UnitTable{2}

\begin{multicols*}{3}[]
	\begin{center}

		\UpgradeGroups{2}{I}

		\specialrules
		\sprule{Very Fast}{This model moves 12" when using
		Advance and 24" when using Rush/Charge.}
		\sprule{Vibration}{When firing this weapon, roll a D6, the result is the AP of the weapon}

	\end{center}
\end{multicols*}

\end{document}
